\subsection{Memory Controller}
The task of the memory controller is to provide valid data for the NN-layers. It communicates with the Block-Ram. The memory controller is responsible for ensuring that the next layer has valid data at all times. The second task of the memory controller is to save the data of the previous data in a free memory address in the Block-RAM. 
\todo{Is it better to have the shiftregister, we discussed last time in the memory controller, because in this case the layer don't have to know anything about the data it gets}

\subsubsection{Interfaces}
\begin{itemize}
	\item S\_LAYER: interface to previous layer
	\item M\_LAYER: interface to next layer 
	\item AXI\_lite: interface to AXI lite bus, is used to read BRAM data directly from processor (slow)
\end{itemize}
\begin{tabular}{|l|l|l|l|l|}
	
	signal & direction & type & width & description\\
	
\end{tabular}

\begin{itemize}
	\item M\_LAYER: interface to next layer
\end{itemize}
\begin{tabular}{|l|l|l|l|l|}
	
	signal & direction & type & width & description\\
	
\end{tabular}

\begin{itemize}
	\item BRAM\_PORTA: write interface to BRAM
\end{itemize}
\begin{tabular}{|l|l|l|l|l|}
	
	signal & direction & type & width & description\\
	
\end{tabular}

\begin{itemize}
	\item BRAM\_PORTB: read interface to BRAM
\end{itemize}
\begin{tabular}{|l|l|l|l|l|}
	
	signal & direction & type & width & description\\
	
\end{tabular}

\subsubsection{Parameter}
\begin{itemize}
	\item PREVIOUS\_LAYER\_TYPE boolean: {TRUE: conv2d, FALSE: dense} % maybe some additional -> integer type
	\item PREVIOUS\_LAYER\_WIDTH integer: {Row length of input matrix} \todo{use extra parameter for dense or simply use width or height, discuss!}
	\item PREVIOUS\_LAYER\_HEIGTH integer: {Column length of input matrix}
	\item PREVIOUS\_LAYER\_CHANNEL integer: {Row length of input matrix}
	\item NEXT\_LAYER\_TYPE boolean: {TRUE: conv2d, FALSE: dense} % maybe some additional -> integer type
	\item NEXT\_LAYER\_WIDTH integer: {Row length of input matrix} \todo{use extra parameter for dense or simply use width or height, discuss!}
	\item NEXT\_LAYER\_HEIGTH integer: {Column length of input matrix}
	\item NEXT\_LAYER\_CHANNEL integer: {Row length of input matrix}
\end{itemize}

\subsection{AXI lite interface}
It is used to read the BRAM data directly from the processor. This can be used for debug purposes. \\
Each memory controller gets an unique address via generics. 
One 32 bit register of the AXI lite bus is used for all memory controller. 
If the processor writes all 0 to the register, debugging mode is deactivated. 
Therefore the memory controller address start with 1 and not with 0.
the 32 bit are separated as follows: \\
\begin{itemize}
	\item 23 downto 0: BRAM address
	\item 27 downto 24: 32 bit vector address 
	\item 31 downto 28 : Memory controller address 
\end{itemize}  
BRAM address: address of the block ram \\
32 bit vector address: If the width of one BRAM register is higher than 32 bit, the 32 bit vector address can be used to select the required part of the vector. \\
Memory controller address: address of the memory controller used in the network starting with 1. If the address of the memory controller is selected debug mode is active. \\

 